cardinalR: Generating interesting high-dimensional data structures

### 2025-04-30 paper-cardinalR.Rmd
Started adding projections for cone data

```{r data-bluntedcone}
cone <- gen_cone(n = 1000, p = 4, h = 5, ratio = 0.5)
```

@@

>>>>

```{r data-bluntedcone, echo=TRUE}
cone <- gen_cone(n = 1000, p = 4, h = 5, ratio = 0.5)
```

@@

```{r cone-proj1}
scaled_data <- scale_data_manual(cone)

## First projection
projection <- cbind(
  c(0.22417,-0.02943,-0.02870,0.08418),
  c(-0.02715,0.18019,0.05053,0.15254))

proj_obj1 <- get_projection(projection = projection, 
                            proj_scale = 1.2, 
                            scaled_data = scaled_data, 
                            axis_param = list(limits = 0.2,
                                              axis_scaled = 3, 
                                              axis_pos_x = -0.2, 
                                              axis_pos_y = -0.2, 
                                              threshold = 0.016))

cone_proj1 <- plot_proj(
  proj_obj = proj_obj1, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.25, 0.25), 
  title = "a1", 
  cex = 2, 
  axis_text_size = 4,
  is_color = FALSE)

```{r cone-proj2}

## Second projection
projection <- cbind(
  c(0.22417,-0.02943,-0.02870,0.08418),
  c(-0.02715,0.18019,0.05053,0.15254))

proj_obj2 <- get_projection(projection = projection, 
                            proj_scale = 1.2, 
                            scaled_data = scaled_data, 
                            axis_param = list(limits = 0.2,
                                              axis_scaled = 3, 
                                              axis_pos_x = -0.2, 
                                              axis_pos_y = -0.2, 
                                              threshold = 0.016))

cone_proj2 <- plot_proj(
  proj_obj = proj_obj2, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.25, 0.15), 
  title = "a1", 
  cex = 2, 
  axis_text_size = 4,
  is_color = FALSE)

```{r cone-proj3}

## Third projection
projection <- cbind(
  c(0.22417,-0.02943,-0.02870,0.08418),
  c(-0.02715,0.18019,0.05053,0.15254))

proj_obj3 <- get_projection(projection = projection, 
                            proj_scale = 1.2, 
                            scaled_data = scaled_data, 
                            axis_param = list(limits = 0.2,
                                              axis_scaled = 3, 
                                              axis_pos_x = -0.2, 
                                              axis_pos_y = -0.2, 
                                              threshold = 0.016))

cone_proj3 <- plot_proj(
  proj_obj = proj_obj3, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.25, 0.15), 
  title = "a1", 
  cex = 2, 
  axis_text_size = 4,
  is_color = FALSE)

```{r, label = "fig-cone-proj", fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `cone` data."}
#| fig-width: 15
#| fig-height: 5

cone_proj1 + cone_proj2 + cone_proj3 +
  plot_layout(ncol = 3, guides = "collect") 
```
